\bfseries\LARGE Vision Vs. LiDAR/Radar Fusion in Autonomous Driving Systems

### 2025-05-25 Papers/Paper One/TopicOne.tex
ammend paper one

This paper evaluates the viability of vision-primary perception systems in autonomous driving, focusing on scalability, efficiency, and environmental resilience. Traditional sensor-fusion architectures based on LiDAR and radar offer high-fidelity spatial mapping but suffer from substantial power consumption, mechanical complexity, and high unit costs, which challenge real-time deployment and mass-market feasibility. Advances in neural perception—particularly transformer-based models and tokenized camera inputs—have enabled camera-only systems to approximate LiDAR-level 3D detection accuracy while operating at a fraction of the computational cost. Benchmark evaluations reveal that vision systems achieve depth estimation errors below three percent and perform within five percent of LiDAR/radar fusion baselines in object detection. Critically, performance gaps in adverse conditions such as fog or night driving are recoverable through the selective integration of millimeter-wave radar. This radar-augmented fallback restores over 80 percent of degraded performance with minimal latency or energy impact. The study advocates for a simplified, vision-first architecture complemented by radar only in edge cases. This paradigm enhances scalability, reduces deployment overhead, and aligns with biologically plausible sensing strategies. LiDAR remains useful for simulation and benchmarking but is unnecessary for live inference.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.7\textwidth]{masking}
	\caption{The Vision Pipeline shows the original camera image, the feature map,
	and the image mask \cite{wang2024}.}
	\label{fig:visionpipe}
\end{figure}

@@

\subsection{Vision as the Core, Radar as the Shield:}

>>>>

This paper evaluates the viability of vision-primary perception systems in
autonomous driving, focusing on scalability, efficiency, and environmental
resilience. Traditional sensor-fusion architectures based on LiDAR and radar
offer high-fidelity spatial mapping but suffer from substantial power
consumption, mechanical complexity, and high unit costs, which challenge
real-time deployment and mass-market feasibility. Advances in neural
perception—particularly transformer-based models and tokenized camera
inputs—have enabled camera-only systems to approximate LiDAR-level 3D detection
accuracy while operating at a fraction of the computational cost. Benchmark
evaluations reveal that vision systems achieve depth estimation errors below
three percent and perform within five percent of LiDAR/Radar fusion baselines in object detection.
Critically, performance gaps in adverse conditions such as fog or night driving are recoverable through the selective integration of millimeter-wave radar. This radar-augmented fallback restores over 80 percent of degraded performance with minimal latency or energy impact. The study advocates for a simplified, vision-first architecture complemented by radar only in edge cases. This paradigm enhances scalability, reduces deployment overhead, and aligns with biologically plausible sensing strategies. LiDAR remains useful for simulation and benchmarking but is unnecessary for live inference.

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\textwidth]{masking}
	\caption{The Vision Pipeline shows the original camera image, the feature map,
	and the image mask \cite{wang2024}.}
	\label{fig:visionpipe}
\end{figure}

@@

\section{Further Discussions}
\subsection{Vision as the Core, Radar as the Shield:}
